\question[1]{A5/1 is $ \dots $}
	{a stream cipher.}
	{a block cipher.}
	{a hash function.}
	{a MAC.}
	
\question[4]{Tick the <strong>correct</strong> assertion regarding GSM.}
	{In GSM, the communication is always encrypted.}
	{The integrity of GSM messages is well protected.}
	{GSM uses the GSME cipher to encrypt messages.}
	{In GSM, the phone is authenticated to the network.}

\question[1]{Tick the <strong>wrong</strong> assertion concerning 3G.}
	{In 3G, the network is authenticated to the phone.}
	{The integrity of 3G messages is well protected.}
	{In 3G, there is a counter to protect against replay attacks.}
	{3G uses f8 for encryption.}

\question[4]{WEP $ \dots $}
	{provides good confidentiality.}
	{provides good message integrity.}
	{provides good authentication.}
	{is badly broken.}
	
\question[3]{Tick the <strong>false</strong> assertion concerning WEP}
	{In WEP, encryption is based on RC4.}
	{In WEP, IVs repeat themselves too often.}
	{In WEP, encryption is based on a block cipher.}
	{WPA-TKIP was designed as a quick fix for WEP.}

\question[2]{Tick the <strong>correct</strong> assertion concerning WPA2}
	{WPA2 uses RC4.}
	{WPA2 uses AES.}
	{WPA2 uses 64-bit keys.}
	{WPA2 is badly broken.}

\question[1]{Tick the <strong>false</strong> assertion concerning WPA-TKIP.}
	{WPA-TKIP uses a fixed RC4 key.}
	{WPA-TKIP avoids replay attacks using a counter.}
	{WPA-TKIP provides much more confidentiality than WEP.}
	{WPA-TKIP doesn't protect well the integrity of the messages.}

\question[3]{Tick the <strong>false</strong> assertion concerning <strong>Bluetooth</strong>.}
{Under reasonable assumptions, pairing is secure if the PIN has high entropy.}
{Under reasonable assumptions, pairing is secure if run through a private
channel.}
{Secure pairing with a dummy device requires the user to select a strong
PIN.}
{Dummy devices share the same long term key with all paired devices.}

\question[4]{Bluetooth is $ \dots $}
		{a long-range wireless technology.}
		{first introduced by vikings.}
		{<strong>not</strong> designed to transmit data.}
		{a short-range wireless technology.}

\question[1]{Bluetooth uses $ \dots $}
		{E0 for encryption.}
		{A5/1 for encryption.}
		{AES for encryption.}
		{RC4 for encryption.}

\question[4]{The encryption in GSM is done by ...}
 {A3.}
 {A8.}
 {E0.}
 {A5.}

 \question[3]{Tick the $ \textbf{false} $ statement regarding 3G.}
 {Confidentiality is preserved. }
 {Message integrity is preserved.}
 {Network is authenticated.}
 {It is secure against replay attacks.}
 
  \question[1]{Tick the $ \textbf{false} $ statement.}
{Cryptographic primitives used in Bluetooth are provably secure.}
{In WEP, authentication is done with the pre-shared keys.}
{The security of Bluetooth 2.0 pairing is  based on PIN.}
{Due to memory limitations, dummy devices can share the same key with everyone.}


 \question[4]{Which of the following is well preserved by 2G?}
 {Confidentiality}
{Message Integrity}
{Challenge freshness}
{Authentication of Mobile Station}

\question[3]{In Bluetooth, the link key $K_{link}$ is  ...}
{used to generate an epheremal key $K_{init}$.}
{not used to generate the encryption key.}
{used to authenticate devices.}
{the input to the pairing protocol.}



\question[4]{Which symmetric key primitive is used in WPA2 encryption?}
{RC4 CBC Mode}
{KASUMI ECB Mode}
{MD5 OFB Mode}
{AES CCM Mode}


\question[1]{Which is  NOT a mobile telephony protocol?}
{WPA}
{DECT}
{EDGE}
{CDMA}

\question[2]{Tick the $ \textbf{false} $ statement. Bluetooth 2.0 Pairing is secure when ...}
{the PIN has a large entropy.}
{it is done only once.}
{it runs in a Faraday cage.}
{it is not used.}

\question[3]{Tick the $ \textbf{false} $ statement. GSM anonymity is broken by ...}
{replaying an A3 challenge.}
{desynchronizing the mobile station and the network.}
{using A5/1.}
{sniffing the very first connection protocol.}

\question[3]{Which protocol does <strong>not</strong> use RC4.}
{WEP}
{WPA}
{WPA2}
{TLS}


\question[2]{Select the <strong>weakest</strong> algorithm.}
{A5/4}
{A5/2}
{A5/3}
{A5/1}

\question[3]{Select the <strong>incorrect</strong> statement. The UMTS improves the security of GSM using}
{authentication of the challenge.}
{integrity protection.}
{A6/1 for encryption.}
{protection against replay attacks.}


\question[3]{Select the <strong>incorrect</strong> statement. Bluetooth is}
{a short-range wireless technology.}
{designed both for data and voice transmission.}
{a standard for RFID tags.}
{able to transmit 1Mbit/sec in 10m distance.}

\question[4]{Select the <strong>incorrect</strong> statement. The Bluetooth project aims for}
{low complexity.}
{low power.}
{low cost.}
{low security.}

\question[3]{Select the <strong>incorrect</strong> statement about Bluetooth. }
 {Privacy protection is weak due to a low entropy in BD\_ADDR.}
 {Bluetooth does not ensure protection against traceability.}
 {The size of frames is unlimited in Bluetooth to reduce the latency.}
 {Sequentiality of frames is not fully ensured.}
 
 \question[4]{Select the <strong>incorrect</strong> statement. Problems in Bluetooth includes:}
 {integrity protection is void.}
 {messages can be erased in radio channel.}
 {privacy protection is weak.}
 {the key of E0 cipher can be recovered within a few seconds.}
 
\question[3]{Select the <strong>incorrect</strong> statement about Bluetooth.}
 {Bluetooth brings various markets together, such as computing and communication.}
 {Pairing leads to a long-term key.}
 {The discovery protocol uses E0 cipher to ensure privacy.}
 {Packets in authentication mode are easily malleable.}

 \question[2]{The problems with WEP with 128 bit key originate from}
 {RC4 being too slow.}
 {an encryption mode weakening RC4.}
 {having a short secret key for RC4.}
 {usage of stream cipher RC4 instead of a CRC32.}
 
 \question[4]{Select the <strong>incorrect</strong> statement. UMTS uses}
 {MILLENAGE for key establishment.}
 {the block cipher KASUMI.}
 {the block cipher AES.}
 {the block cipher DES.}
 
 \question[3]{Bluetooth pairing v2.0 is based on$ \dots $}
{bilinar mappings over elliptic curves.}
{a short authenticated string.}
{an ephemeral secret PIN code.}
{a secure token.}

\question[3]{Tick the <strong>false</strong> assertion. Bluetooth$ \dots $}
{uses a stream cipher for encryption.}
{has weak message integrity protection for secure communication.}
{has dummy devices which use the same secret key with any other device.}
{uses the SAFER+ block cipher in a one-way mode.}

\question[4]{To protect against the insecurity of a Bluetooth headset, the best strategy is to$ \dots $}
{put it in a metalic bag.}
{Use random 64-bit PINs.}
{switch it off when it is not being used.}
{never leave it unattended.}

 \question[3]{Which protocol is used for encryption in GSM?}
 {A3}
 {A4}
 {A5}
 {A8}

\question[1]{How is data integrity ensured in WEP?}
{there is no integrity.}
{A3.}
{Michael.}
{HMAC.}

\question[2]{What is the number of secret bits in a WEP key?}
{64 or 128 bits.}
{40 or 104 bits.}
{64 or 128 bytes.}
{40 or 104 bytes.}

\question[2]{The complexity of generating a 2-byte keystream of RC4 is$ \dots $}
{$1\cdot\mathrm{KSA} + 1\cdot\mathrm{PRGA}$.}
{$1\cdot\mathrm{KSA}+ 2\cdot\mathrm{PRGA}$.}
{$2\cdot\mathrm{KSA}+ 1\cdot\mathrm{PRGA}$.}
{$2\cdot\mathrm{KSA}+ 2\cdot\mathrm{PRGA}$.}

\question[2]{Consider a mobile station (MS) with a SIM card associated to a home network (HN). The MS tries to connect to a visited network (VN). In the GSM authentication, who knows the key $K_i$?}%
{SIM only.}%
{SIM and HN.}%
{SIM, MS and HN.}%
{SIM, MS, VN and HN.}%

\question[2]{Tick the <strong>false</strong> assertion about Bluetooth.}
{The term Bluetooth comes from a Viking King of the 10th Century.}
{Bluetooth was developped by Microsoft.}
{The specifications of Bluetooth 2.1 have already been released.}
{Bluetooth was designed for a variety of mobile devices.}

\question[4]{During a Bluetooth pairing, we use an extra channel to transmit the PIN. Which assumptions are required on this extra channel?}%
{None.}%
{Authenticity only.}%
{Authenticity and integrity only.}%
{Confidentiality, authenticity, and integrity.}%

\question[3]{During a Bluetooth pairing with a dummy device, we assume that $ \ldots $}%
{the PIN is transmitted securely.}%
{the device can use GSM communication.}%
{the pairing is made in a bunker.}%
{the telephony operator is able to authenticate the device.}%

\question[1]{During a Bluetooth pairing with a dummy device, $ \ldots $}%
{the link key is forced to be the unit key.}%
{the link key and unit key are totaly differents.}%
{there is no key.}%
{the unit key is forced to be the link key.}%

\question[4]{Tick the <strong>false</strong> assertion.}
{E0 is a Bluetooth standard.}
{E0 makes use of LFSR.}
{E0 is a stream cipher.}
{E0 is based on RC4.}

\question[3]{In the GSM infrastructure, which of the following entity contains Ki?}
{MS (Mobile Station)}
{VLR (Visitor Location Register)}
{SIM (Subscriber Identity Module)}
{TGS (Ticket Granting Server)}

\question[2]{Tick the <strong>false</strong> assertion about Bluetooth.}
{The term Bluetooth comes from a Viking King of the 10th Century.}
{The mode 1 of Bluetooth is secure.}
{The specifications of Bluetooth 2.0 have already been released.}
{Bluetooth was designed for a variety of mobile devices.}

\question[2]{Tick the <strong>false</strong> assertion about Bluetooth.}
 {The Bluetooth Pairing does not rely on any public key algorithm.}
 {When connecting a dummy device to a normal device, the normal device generates the link key.}
 {The range of the encryption keys used goes from 8 to 128 bits.}
 {After the pairing protocol, two bluetooth devices share a common secret key.}

\question[2]{In the MILENAGE Protocol,  the algorithm f9 (MAC) is based on ...}
 {KATAN.}
 {KASUMI.}
 {DES.}
 {RC5.}

\question[1]{Tick the $ \textbf{false} $ statement.}
{In the  key exchange phase, two parties exchange their secret keys.}
{In encryption, the ciphertext space must be at least as big as the plaintext space.}
{Key agreement and key exchange are equivalent  notions.}
{ElGamal is based on the hardness of the Discrete Logarithm Problem. }

 \question[4]{Which is NOT related to RSA?}
{PKCS{\#}1v1.5}
{OAEP}
{ISO/IEC 9796}
{DSA}

\question[2]{Which signature has message recovery? }
{The ECDSA Signature }
{The Plain RSA Signature}
{The Schnorr Signature}
{The Pointcheval-Vaudenay Signature}

\question[4]{Redundancy is added to the plaintext in the Plain Rabin Encryption Scheme in order to}
{increase the size of the plaintext.}
{increase the security.}
{have non-deterministic encryption.}
{get rid of ambiguity in the decryption.}

\question[1]{Which of the following satisfies \textit{forward secrecy}?}
{RFC 2631 ephemeral-ephemeral mode}
{AES ECB mode}
{PKCS{\#}1v1.5 }
{RSA-OAEP }

\question[4]{Tick the $ \textbf{false} $ statement regarding RSA-PSS.}
{It is a signature scheme using RSA and a hash function.}
{It is based on the difficulty of the Factoring Problem.}
{It requires a good hash function.}
{It is a new encryption mode for RSA.}

\question[3]{Tick the $ \textbf{true} $ statement regarding Rabin Cryptosystem.}
{It is based on the Discrete Logarithm Problem.}
{The sender needs to know the factorization of modulus $N$.}
{The receiver needs to know the factorization of modulus $N$.}
{It is secure if and only if $\mathbb{Z}_{N}^* \approx \mathbb{Z}_{N-1}$.}

\question[2]{Tick the $ \textbf{false} $ statement regarding message authentication based on public key techniques.}
{It is called \textit{digital signature}.}
{It achieves perfect secrecy by using the Vernam Cipher.}
{It is used to authenticate public keys.}
{It can be realized using RSA and ElGamal.}

\question[4]{What could we recommend as an RSA modulus for both security and efficiency?}
{64 bits}
{128 bits}
{512 bits}
{1024 bits}

\question[2]{S/Key is $ \ldots $}%
{an encryption scheme used in GSM.}%
{a one-time password based protocol.}%
{a secret key used in Bluetooth.}%
{a secret key involved in Kerberos.}%

\question[4]{Using salt for UNIX passwords $ \ldots $}
{allows to speed up the verification for the server.}
{makes the protocol secure against computationally unbounded adversary.}
{allows to transmit the password over a non confidential channel without compromising the security.}
{helps preventing dictionary attacks.}

\question[3]{Which cryptographic primitive(s) is (are) used in S/Key - OTP ?}
{Only encryption and a hash function}       
{Only encryption and a MAC algorithm}            
{Only a hash function}            
{Only a MAC}  




 


	
	