\question[2]{A biometric passport can be distinguished from a classical one by$ \dots $}
{the writing ``Biometric Passport'' on the cover.}
{a specific logo on the cover.}
{checking the creation date of the passport.}
{the color of the passport.}

\question[3]{Tick the <strong>false</strong> assertion. A metal cover$ \dots $}
{should protect the passport from being accessed when closed.}
{makes the passport ring at security gates.}
{is sufficient to garantee the privacy of the information contained in the passport.}
{is used in passports issued by the USA.}

\question[4]{Which cryptographic primitive is <strong>not</strong> used in biometric passports?}
{message authenthication codes.}
{symmetric encryption.}
{hash functions.}
{public-key encryption.}

\question[1]{There are several crypto protocols used by a biometric passport as defined in the standard. Which one is <strong>not</strong> one of them?}
{raw access control}
{basic access control}
{extended access control}
{passive authentication}

\question[3]{Which biometric technology is always used in <strong>current</strong> biometric passports?}
{face recognition}
{fingerprint}
{iris recognition}
{speech recognition}

\question[3]{Tick the <strong>false</strong> assertion about the SO$_D$.}
{it is used to check the integrity of the LDS}
{it contains a list of hashes of data DG1-DG15}
{it contains a certificate and a signature.}
{it is only used in passports issued by the USA.}

\question[1]{From the random number sent by the passport, an adversary may be able to deduce$ \dots $}
{the country which has issued the passport.}
{the identity of the holder of the passport.}
{the hash of the biometric data contained in the passport.}
{the expiration date of the passport.}

\question[2]{In BAC, the MRZ\_info needed to perfom the authenticated key exchange phase consists of 21 characters. However, it may have an entropy of only 47 bits in reality. Why?}
{Because a random password of this length has only 47 bits of entropy.}
{Because MRZ\_info only depends on parameters with low entropy.}
{Because the passport transmits several bits of its MRZ\_info in clear.}
{Because the reader transmits several bits of the passport's MRZ\_info in clear.}

\question[1]{In EAC, the authentication protocol is based on$ \dots $}
{A semi-static Diffie-Hellman protocol with an authenticated key.}
{A RSA signature.}
{the SO$_D$.}
{a short authenticated string (SAS) based key agreement protocol}

\question[1]{Tick the <strong>false</strong> assertion. Non-transferable authentication would be a good alternative to current protocols because$ \dots $ }
{no PKI is needed.}
{only a legitimate reader can authenticate the passport.}
{it thwart the mafia fraud attack.}
{it considers malicious readers having access to the PKI.}