\question[1]{Tick the $ \textbf{true} $ statement regarding $\mathsf{GF}(2^k)$.}
 {Addition is performed as bitwise XOR.}
 {Multiplication is performed modulo $2^k$.}
 {It has order $\varphi(2^k)$.}
 {Its characteristic is $k$.}
 
  \question[4]{Tick the $ \textbf{true} $ statement.}
 {In $\mathbb{Z}_p^*$, there are $\varphi(p)$ generators.}
 {$(\mathsf{GF}(7)^*, \times)$ is isomorphic to ($\mathbb{Z}_7,+$).}
 {The probability that $N$ is prime is $\frac{1}{N\ln N}$.}
 {For any prime power $p^k$, there exists a finite field of cardinality $p^k$.}
 
  \question[4]{Tick the $ \textbf{false} $ statement.}
 {The cardinality of $E_{a,b}(\mathsf{GF}(q))$ is bounded by $q+1+2\sqrt{q}$.}
 {$E_{a,b}$ is non-singular if $4a^3+27b^2 \neq 0$ over a finite field of characteristic $p>3$.}
 {In $(\mathsf{GF}(2^k))$, we have $\mathsf{Tr}(a+b)=\mathsf{Tr}(a)+\mathsf{Tr}(b)$.}
 {Two Elliptic curves cannot have the same $j$-invariant.}
 
  \question[2]{Tick the $ \textbf{false} $ statement.}
 {The identity element of $E_{a,b}$ is the point at infinity.}
 {If a point is singular on an Elliptic curve, we can draw a tangent to this point.}
 { $P=(x_p,y_p)$ and $Q=(x_p,-y_p)$ are the inverse of each other on an Elliptic curve of equation $y^3=x^3+ax+b$.}
 {Elliptic curve cryptography is useful in public-key cryptography.}
 
 \question[4]{Select the \emph{correct} statement.}
{$\mathbb{Z}_{pq}$ is a field, for $p,q$ primes.}
{$\mathbb{Z}_{p^q}$ is a field, for $p$ prime $q$ integer.}
{$GF(pq)$ is a field, for $p,q$ primes.}
{$GF(p^q)$ is a field, for $p$ prime $q$ integer.}

\question[3]{Choose the \emph{correct} statement}
 {Elliptic curves form a field.}
 {Elliptic curves form a ring.}
 {Elliptic curves form an Abelian group.}
 {Elliptic curves form an ideal.}
 
 \question[3]{Choose the \emph{incorrect} statement}
 {The cardinality of an elliptic curve can be bounded using Hasse theorem.}
 {Elliptic curves are defined over a finite field.}
 {Elliptic curves are defined over an Abelian group.}
 {Points on elliptic curves satisfy a cubic polynomial equation.}
 
 \question[3]{Mark the \emph{incorrect} statement. A finite field is}
 {always isomorphic to $\mathsf{GF}(p^k)$, for some prime $p$ and integer $k$.}
 {always isomorphic to $\mathbb{Z}_p[x]/Q(x)$, for some  prime $p$ and an irreducible polynomial $Q$.}
 {always isomorphic to $\mathbb{Z}_{p^k}$, for a prime $p$ and integer $k$.}
 {unique up to an isomorphism.}
 
 
 \question[3]{Which one of the following polynomials in $\mathrm{GF}(2^3)$ is irreducible?}
 {$P(x)=x^2$}
 {$P(x)=x^2+1$}
 {$P(x)=x^3+x+1$}
 {$P(x)=x^3+x^2+x+1$}
 
 \question[1]{$\mathrm{GF}(2^k)$ is represented by the set of$ \dots $}
 {polynomials of degree at most $k-1$ with binary coefficients.}
 {polynomials of degree at most $k-1$ with coefficients in $\mathbb{Z}_k$.}
 {polynomials of degree at most $2^k$ with coefficients in $\mathbb{Z}$.}
 {polynomials of degree at most $2$ with coefficients in $\mathbb{Z}_k$.}
 
 \question[1]{Let $p$ be a prime number and $n$ be an integer. What is the order of $\mathrm{GF}(p^n)$?}
{$p^n$}
{$p^n-1$}
{$p^{n-1}$} 
{$1-p^n$}