\question[1]{Consider the following pairs of AES operations. In which, the order of the two operations does <strong>not</strong> matter?}
 {SubBytes-ShiftRows}
 {AddRoundKey-MixColumn}
 {SubBytes-MixColumn}
 {SubBytes-AddRoundKey}
 
  \question[3]{Tick the $ \textbf{false} $ statement regarding the DES round function.}
 {There is an expansion operation $E$ from 32 to 48 bits.}
{A round key is XORed to an internal register.}
{There are $8$ identical S-boxes (substitution boxes) of size $6 \times 4$.}
 {There is a permutation $P$ on 32-bits.}
 
 \question[2]{Which mode of operation is similar to a stream cipher?}
 {ECB}
 {OFB}
 {CFB}
 {CBC}
 
 
  \question[2]{Ciphertext stealing ... }
 {results in the expansion  of the plaintext.}
 {prevents the expansion of the ciphertext.}
 {requires an additional secret key.}
 {steals ciphertext which results in lack of encrypted data.}
 
  \question[4] {Tick the <strong>false</strong> assertion.}
 {The Rijndael design contains S-boxes.}
 {The Rijndael design uses $\text{GF}(2^8)$ arithmetics.}
 {The Rijndael design contains a linear layer --- ShiftRows and MixColumn.}
 {The Rijndael design is based on one-way functions.}
 
\question[3]{CCM}
{is a block cipher.}
{is a hash function.}
{is an authenticated mode of operation.}
{stands for coded ciphertext mode.}
	
\question[3]{What is the average complexity of exhaustive search when the key is distributed uniformly at random over $N$ keys?}
 {$\log N$}
 {$2^N$}
 {$\frac{N+1}{2}$}
 {$\sqrt{N}$}
 
 \question[2]{Select the <strong>incorrect</strong> statement. The brute force attack $ \dots $}
 {can be applicable after decades according to Moore's law.}
 {can break a cipher with a $128$-bit key on your PC today.}
 {has higher worst case complexity than average case complexity.}
 {refers to a way of getting the secret key, exhaustively.}

\question[1]{What are the complexities for the single-target dictionary attacks, when there are $N$ keys?}
{Preprocessing: $N$, Memory: $N$, Time: 1 }
{Preprocessing: $N$, Memory: $1$, Time: $N$ }
{Preprocessing: $1$, Memory: $N$, Time: $N$ }
{Preprocessing: $0$, Memory: $1$, Time: $\sqrt{N}$ }

\question[1]{Select the <strong>incorrect</strong> statement.}
{Double DES is much more secure than single DES.}
{Double DES is as secure as two-key triple DES.}
{Three-key triple DES is more secure than two-key triple DES.}
{Multiple encryptions are not always much more secure than a single encryption.}

\question[3]{Which scheme is the most secure?}
{DES.}
{Two-key triple DES.}
{Three-key triple DES.}
{Double DES.}
	
\question[4]{Which key size is not supported by AES?}  
{256 bits}
{192 bits}
{128 bits}
{64 bits}

\question[1]{Tick the $ \textbf{false} $ statement.}
{A5/1 is a secure block cipher.}
 {DES uses the Feistel scheme with a non-invertible round function.}
 {AES is a secure block cipher which is used in many cryptographic applications.}
 {RC4 is used in WEP. }
 
 \question[2]{Tick the $ \textbf{false} $ statement regarding Modes of Operation in Block ciphers.}
{The CBC mode uses an IV value.}
{The ECB mode is a secure way to use block ciphers using a single key.}
{The CTR mode uses a counter which is new for every block.}
{The OFB mode transforms a block cipher into a stream cipher.}

\question[4]{In which attack scenario does the adversary ask for the decryption of selected messages? }
{Known plaintext attack}
{Chosen plaintext attack}
{Ciphertext only attack}
{Chosen ciphertext attack}

\question[3]{Which cipher is AES?}
{SAFER}
{BLOWFISH}
{RIJNDAEL}
{RC5}

\question[2]{A constant initialization vector (IV), i.e., same for every plaintext, can be used in the ...}
{CTR mode.}
 {CBC mode.}
 {OFB mode.}
 {ECB mode.}
 

\question[3]{ Two-Key Triple-DES is attacked by an algorithm based on ...}
{Birthday Paradox.}
{AES.}
{the Meet-in-the-Middle Attack.}
{the Factoring.}

\question[1]{The needed number of DES operations to attack DES is about ...}
{$2^{54}.$}
{$2^{64}.$}
{$2^{128}.$}
{$2^{256}.$}

 \question[4]{Select the <strong>incorrect</strong> statement.}
 {The OFB mode requires an IV.}
 {The CBC mode requires an IV.}
 {The CFB mode requires an IV.}
 {The ECB mode requires an IV.}
 
 
\question[4]{Select <strong>incorrect</strong> statement. The exhaustive search}
{can be used to find a secret key of AES.}
{is a brute force attack.}
{is not applicable against perfectly secure cipher.}
{runs in time polynomial in the length of the key.}

\question[4]{Select <strong>incorrect</strong> statement. Complexity analysis of an attack consideres }
{time complexity.}
{memory complexity.}
{probability of success.}
{difficulty to understand a corresponding journal paper.}

\question[3]{Select <strong>correct</strong> statement. The brute force attack}
{is always applicable after few years according to Moore's law.}
{should always perform better than any dedicated attack.}
{should have exponential complexity for a good cipher.}
{refers to an attack of an adversary against the holder of secret key.}

\question[2]{Select <strong>incorrect</strong> statement. Generic attacks on DES include}
{time memory tradeof against 2 key Triple DES.}
{collision attack against 3 key Triple DES.}
{meet in the middle attack against 3 key Triple DES.}
{known plaintext attack by Van Oorschot-Wiener agains 2 key Triple DES.}

\question[3]{Select <strong>incorrect</strong> statement. The complexity analysis usually considers}
{worst case complexity of the attack.}
{average case of the attack.}
{best case complexity of the attack.}
{none of the above.}

\question[4]{Select <strong>incorrect</strong> statement. The brute force technique against a cipher with key $256$ bits is}
{impossible even if we can compute without burning an energy.}
{impossible since the number of possible keys is too high $2^{256} \approx 10^{77}$.}
{impossible in future even if we consider Moore's law.}
{feasible using all clusters at EPFL.}

\question[4]{Why do block ciphers use modes of operation?}
 {it is necessary for the decryption to work.}
 {to be provably secure.}
 {to use keys of any size.}
 {to encrypt messages of any size.}
 
 \question[3]{Which one of these is <strong>not</strong> a skeleton used to design block ciphers?}
 {a Feistel scheme}%
 {a Subsitution-permutation network}%
 {a Merkle-Damg{\aa}rd construction}%
 {a Lay-Massey Scheme}%
 

 \question[1]{Let $f_K:\{0,1\}^k\to\{0,1\}^\ell$ be a family of functions. Under which assumption $f_K$ <strong>can not</strong> define a block cipher?}%
 {$k > \ell$.}
 {$k=\ell-1$.}
 {$k=\ell$.}
 {$k=\ell/2$.}

 \question[1]{Which one of these is <strong>not</strong> a stream cipher?}%
 {IDEA}%
 {RC4}%
 {A5/1}%
 {E0}%
 
 \question[3]{Tick the <strong>false</strong> assertion. Using double encryption leads to$ \dots $}
{doubling the complexity of the Encryption algorithm.}
{doubling the complexity of the Decryption algorithm.}
{doubling the complexity of all the attacks against the cipher.}
{doubling the length of the key.}

\question[3]{Tick the <strong>false</strong> assertion. Two-keys triple DES$ \dots $}
{is more secure than double encryption.}
{is less secure than AES.}
{is as secure as a block cipher using a key twice longer.}
{is vulnerable to a certain variant of a meet-in-the-middle attacks.}

\question[2]{If we have a $n$-bit key, 
the attack phase with time-memory tradeoff will roughly have$ \dots $}
{a time complexity of $1$ (constant).}
{a time complexity of $2^{\frac{2}{3}n}$}
{a time complexity of $2^{\frac{n}{2}}$}
{a time complexity of $2^{n}$}

\question[1]{Which one of these is the least memory consuming attack?}
{Exhaustive search.}
{Dictionnary attack.}
{Time-memory tradeoff.}
{Time-memory tradeoff with a rainbow table.}

\question[3]{In the AES MixColumns procedure, a byte represents $ \ldots $}
{a polynomial of degree less than 16 with coefficients in $\mathbf{Z}_2$}
{a polynomial of degree less than  4 with coefficients in $\mathbf{Z}_4$}
{a polynomial of degree less than  8 with coefficients in $\mathbf{Z}_2$}
{an integer between 0 and 255.}

\question[2]{LFSRs are used within $ \ldots $}
{IDEA}
{A5/1}
{AES}
{SAFER}


\question[3]{What is the length in bits of the input and output of a DES S-Box respectively?}
{6 and 6}
{4 and 6}
{6 and 4}
{4 and 4}

\question[2]{Tick the <strong>false</strong> assertion.}
{A Feistel scheme is invertible even if the round functions are not injective.}
{A Feistel scheme is not invertible if the round functions are not surjective.}
{A Feistel scheme is an involution if the round functions are all identical.}
{The name of Feistel schemes goes back to the LUCIFER cipher.}

\question[4]{Which of the following terms represents a mode of operation which transforms a block cipher into a stream cipher?} 
{3DES} 
{CBC}
{ECB} 
{CTR}

\question[2]{What is the worst-case complexity of an exhaustive key search attack against a block cipher having a 64-bit key and 128-bit blocks?}  
{$2^{128}$}
{$2^{64}$}
{$2^{96}$}
{$2^{127}$}

\question[3]{Which of the following algorithms is a stream cipher?}
{FOX}
{IDEA}
{RC4}
{AES}

\question[2]{Tick the true assertion.}
{A dictionary attack requires less memory than a time-memory tradeoff.}
{Double-DES succumbs under a Meet-in-the-Middle attack.}
{AES is the ancestor of DES.}
{IDEA has the same round functions as DES.}
  
  
 \question[1]{One of the following ciphers is a <strong>block</strong> cipher. Which one?}
  {AES}
  {RC4} 
  {A5/1}
  {MD5}
  
 \question[3]{The DES key schedule$ \dots $}
 {$ \dots $ is based on a Feistel scheme.}
 {$ \dots $ takes as an input a key of 128 bits.}
 {$ \dots $ generates 16 subkeys.}
 {$ \dots $ in only used during the encryption phase, not during the decryption phase.}
	
\question[3]{Which of the following acronyms does not designate a mode of operation?}
 {CBC}  
 {CTR} 
 {CRC}
 {ECB}
 
 
 \question[4]{Stream ciphers$ \dots $}
 {$ \dots $ are intended to be implemented in software.}
 {$ \dots $ are more secure than block ciphers, in general.}
 {$ \dots $ use a key to encrypt and a <strong>different</strong> key to decrypt.}
 {$ \dots $ are based on the Vernam cipher.}
 
 
 \question[4]{Which of the following operation is not part of AES?}
 {AddRoundKey}
 {SubBytes}
 {MixColumns}
 {MulRoundKey}
 
 \question[2]{Tick the <strong>false</strong> answer about the CTR mode of operation.}
 {The CTR mode turns a block cipher into a stream cipher.}
 {The initial clock value should always start at 0 for the encryption of two successive plaintexts.}
 {Encryption and decryption are identical algorithms.}
 {It can be used with any secure block cipher.}
 
 \question[2]{AES$ \dots $}
{$ \dots $ has a variable key length <strong>and</strong> a variable block length.}
{$ \dots $ has a variable key length <strong>and</strong> a fixed block length.}
{$ \dots $ has a fixed key length <strong>and</strong> a variable block length.}
{$ \dots $ has a fixed key length <strong>and</strong> a fixed block length.}
 
 \question[3]{An element of the finite field $\mathrm{GF}(2^8)$ is usually represented by$ \dots $}
 {$ \dots $ one hexadecimal digit.}
 {$ \dots $ eight bytes.}
 {$ \dots $ two hexadecimal digits.}
 {$ \dots $ an irreducible polynomial of degree 8.}
 
\question[1]{Which of the following ciphers is based on arithmetics over the finite field $\mathrm{GF}(2^8)$?}
{AES}
{DES}
{A5/1}
{RC4}

\question[1]{The Advanced Encryption Standard (AES) is based on arithmetics on$ \dots $}
{$\mathrm{GF}(256)$} 
{$\mathbf{Z}_{2^8}^*$} 
{$\mathbf{Q}\setminus \{0\}$}
{$\mathbf{Z}_{2^8}$}


\question[1]{Select <strong>incorrect</strong> statement. }
{The high entropy of password is ensured by hashing the password before storing.}
{A random salt provides some level of protection against dictionary attack.}
{A password of length $8$ characters should contain non-alphanumerical characters in order to be non-recoverable by brute force.}
{A special purpose device can recover $56$ bit passwords in a matter of minutes.}

\question[2]{Because of Moore's law, we have to$ \dots $}
{double the size of the symmetric keys we use every 18 months.}
{increase the size of the symmetric keys we use by 1 bit every 18 months.}
{change an AES key every 18 months.}
{stop using AES by 2012.}

\question[4]{Which assumption(s) is (are) required during the exchange of a key which will be used by a block cipher?}%
{Nothing.}
{Authentication.}
{Authentication and integrity.}
{Confidentiality.}

\question[2]{Which one is <strong>not</strong> a block cipher?}%
{DES}
{ECB}
{SAFER}
{IDEA}

\question[1]{Consider a twelve-round Feistel scheme $\Psi(F^{k_1},F^{k_2},$ \dots $,F^{k_{12}})$.  Tick the <strong>minimal necessary</strong> condition for $\Psi$ to be a permutation:}%
{$F^{k_i}$ are functions}%
{$F^{k_i}$ are injective functions}%
{$F^{k_i}$ are surjective functions}%
{$F^{k_i}$ are bijective functions}%

\question[2]{CBC can deal with three types of IV. Tick the <strong>false</strong> answer.}
{A random IV sent in clear.}%
{A secret random IV which is sent encrypted.}%
{A non secret constant IV.}%
{A secret IV which is part of the key.}%

\question[4]{Which one is a stream cipher?}%
{RSA}%
{MD5}%
{AES}%
{RC4}%

\question[3]{Stream ciphers often use a nonce to $ \dots $}%
{simplify the key schedule.}%
{reduce the size of the secret key.}%
{avoid the reuse of the key stream.}%
{improve the efficiency of the automaton.}%

\question[2]{Consider Double DES and two-key Triple DES. Tick the right answer.}%
{A meet-in-the-middle attack is useless.}%
{A meet-in-the-middle attack breaks Double DES only.}%
{A meet-in-the-middle attack breaks Triple DES only.}%
{A meet-in-the-middle attack breaks Double DES and Triple DES.}%

\question[3]{The worst case complexity of an exaustive search against DES is$ \dots $}%
{$1$}%
{$\frac{2^{64}}{2}$}%
{$2^{56}$}%
{$2^{64}$}%

\question[1]{Which of the following attacks needs no precomputation.}%
{Exhaustive search.}%
{Dictionary attack.}%
{Meet-in-the-middle attack.}%
{A time memory tradeoff.}%


